---
title: "Alcohol vs Seat choice"
author: "Mikaela Elias"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
##Our goal is to answer this question     
          
Is there a difference between the alcohol consumed between the row in which is sat in?      
        
##Methods           
Predict alcohol consumption based on where you sit       
       
 $H_0$ there is no difference between amount of alcohol consumed and where you sit     
 $H_A$ there is a difference between the amount of alcohol consumed and where you sit    
      
Alcohol~Seat  
  
Alcohol is numerical , Seat is categorical       
    
We will use the helper file    
Numerical~Categorical     


## Now add in boxplot
```{r}
basicCN <- ggplot(davisdata,aes(x=Seat,y=alcohol))
```
```{r}
basicCN + geom_boxplot()
```
          
The boxplot shows that students that sit in the back are more likely to consume more alcohol than those who sit in the middle and the front. 
            
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
           
The fancy notch boxplot shows that students who sit in the back are more likely than those who sit in the middle or the front.  
          
## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
            
The numerical summary shows that student who sit in the back are 4.788 times more likely to consume more alcohol than those who sit in the front. It also shows that students who sit in the back are 1.437 times more likely to consume more alcohol than those who sit in the middle. 
          
## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
          
The Aov test shows that the p-value is 0.000116 which is less than 0.5 so I will reject the null hypothesis. 
          
I conclude that there is a difference in amount of alcohol consumed based on seating. 
          
## Conclusions
        
The question is: Is there a difference between the alcohol consumed between the row in which is sat in?

 $H_0$ there is no difference between amount of alcohol consumed and where you sit     
 $H_A$ there is a difference between the amount of alcohol consumed and where you sit 
 
 I reject the null hypothesis because...           
The boxplot shows that students that sit in the back are more likely to consume more alcohol than those who sit in the middle and the front.           
The fancy notch boxplot shows that students who sit in the back are more likely than those who sit in the middle or the front.            
The numerical summary shows that student who sit in the back are 4.788 times more likely to consume more alcohol than those who sit in the front. It also shows that students who sit in the back are 1.437 times more likely to consume more alcohol than those who sit in the middle.       
The Aov test shows that the p-value is 0.000116 which is less than 0.5 so I will reject the null hypothesis. 
          
I conclude that there is a difference in amount of alcohol consumed based on seating.
